# Data Transformation

We'd like to order the data by `average_review` to see the general ranking of the restaurants.

```{r}
data <- read.csv("restaurant.csv", encoding = "UTF-8")
data <- data[order(data$average_review, decreasing = TRUE),]
head(data)
```
We'd like to join our datasets to see both the violations and the ratings. To accomplish that, we first convert all restaurants names to lower cases with `tolower()`, then strip symbols off on two datasets with `sub()` to create uniform syntax for names. After that, we used `sqldf` package to count the number of violations each restaurant has and join the two datasets together as our final dataset.

```{r}

data$name <- tolower(data$name)
data$name<-sub("\\-.*", "", data$name)

violations <- read.csv(file = 'violations.csv')

violations$DBA <- tolower(violations$DBA)
violations$DBA <- sub("\\(.*",'',violations$DBA)

library(sqldf)

violation_counts <- sqldf('select DBA,count(DBA) as violation_count from violations group by DBA')

df <- sqldf('select * from data as d join violation_counts as v on d.name = v.DBA')
```
We can take a glance at the final dataset.

```{r}
df$DBA <- NULL

head(df,3)
write.csv(df, './finaldf.csv', row.names=FALSE)
```
